%% Example CV template
%% This file is intentionally generic. Run the profile setup workflow to
%% populate a private, personalized CV locally.
%%
%% Compile with: lualatex main_example.tex

\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}

\renewcommand*{\firstnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\lastnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\sectionstyle}[1]{{\sectionfont\color{color1}#1}}

\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=blue,
    pdftitle={Candidate CV},
    pdfpagemode=FullScreen,
}
\usepackage[scale=0.80]{geometry}

% Personal data - replace locally, do not commit private details.
\name{First}{Last}
\address{City, Country}{}{}
\phone[mobile]{+00 000 000 000}
\email{name@example.com}
\extrainfo{Language 1 \& Language 2}

\begin{document}

\makecvtitle

\vspace{6pt}
\small{Senior technology and product leader with experience in delivery, stakeholder coordination, team scaling, and business-facing technical execution. Replace this summary with a truthful, role-specific profile generated from your private profile files.}

\section{Core Competencies}
\vspace{1pt}
\begin{itemize}
\item \textbf{Technology Leadership}: Team scaling, technical planning, delivery ownership, and engineering management.
\item \textbf{Product \& Delivery}: Product ownership, roadmap coordination, agile delivery, and KPI alignment.
\item \textbf{AI Automation}: Workflow automation, AI-assisted development, agentic systems, API integrations, and business process improvement.
\item \textbf{Business-Facing Execution}: Stakeholder communication, requirements discovery, solution scoping, and delivery risk management.
\end{itemize}

\section{Professional Experience}
\vspace{3pt}
\begin{itemize}

\item{\cventry{YYYY--YYYY}{Role Title}{Company Name}{Location}{}{\vspace{1pt}
\begin{itemize}
    \item Describe a verified achievement with scope, action, and impact.
    \item Include technologies, domains, and business outcomes only when true.
    \item Quantify results where possible.
\end{itemize}}}

\vspace{3pt}

\item{\cventry{YYYY--YYYY}{Previous Role Title}{Previous Company}{Location}{}{\vspace{1pt}
\begin{itemize}
    \item Describe delivery, product, leadership, or technical responsibilities.
    \item Reorder bullets when tailoring the CV to a specific role.
\end{itemize}}}

\end{itemize}

\section{Education \& Certifications}
\vspace{1pt}
\begin{itemize}
\item{\cventry{YYYY--YYYY}{Degree or Certification}{Institution}{}{}{Relevant focus areas.}}
\item \textbf{Certification Name} (YYYY).
\end{itemize}

\section{Languages}
\vspace{1pt}
\begin{itemize}
\item Language 1 and Language 2. Add proficiency levels when confirmed.
\end{itemize}

\section{References}
\vspace{1pt}
\begin{itemize}
\item{Available upon request.}
\end{itemize}

\end{document}
